Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications

### 2025-12-06 Submission.tex
hudson dunn bros

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\makeatother
\keywords{O*NET, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications},
  pdfauthor={Alicia Stachowski2, John Kulas1, \& Renata García Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={O*NET, challenge-hindrance framework, job demands-resources, job characteristics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
Discussions of job characteristics often include a tacit characterization that these job elements are either resources or demands. The current study documents variability in ratings of O*NET specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes. We additionally explore the potential moderating role of resources on these relationships. Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, what is viewed as challenging is also commonly be interpreted as resourceful. Furthermore, greater experienced resources moderate the challenge--engagement relationship as well as the hindrance-stress and hindrance--burnout relationships. These findings broadly support the non--mutually exclusive perspective on job characteristic appraisal as well as multiple theoretically--specified outcome associations.
}

@@

\subsection{Theoretical Foundations}\label{theoretical-foundations}

Job demands-resources theory (e.g., Bakker \& Demerouti, 2014; 2017) highlights the importance of demands and resources on the employee experience of motivation and strain as well as other, less proximal outcomes. Resources include physical, psychological, social, or organizational aspects of jobs that help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker and Demerouti, 2014, 2017). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001). The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).

Cavanaugh et al. (2000) extended this framework by proposing a distinction between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}. Challenge demands promote mastery, personal growth, and future gains. These demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility (LePine, 2022). Hindrance demands, in contrast, inhibit growth, learning, and the general achievement of goals. Example hindrance demands that have been previously noted include role conflict and role ambiguity (LePine, 2022).

LePine (2022) deconstructs the mechanisms by which demands are related to performance and wellbeing outcomes. First, demands appraised as \emph{challenges} typically result in a more positive appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Demands appraised as \emph{hindrances} elicit a different process. Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other negative affect--laden reactions (LePine, 2022).

Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, LePine et al. (2005) regarding performance and Crawford et al. (2010) regarding engagement). Pindek et al. (2024) meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by LePine (2022) above). As expected, hindrance demands had both direct and indirect (through strain) associations with performance (Pindek et al., 2024).

Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. Pindek et al. (2024) notes these \emph{a priori} classification of characteristics as demands, challenges, or hindrances as a methdological limitation, as do Horan et al. (2020). In fact, although much of our research on job demands is based on such exclusive classifications (Searle and Auton, 2015), the most recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., two different employees could most certainly perceive ``daily interaction with co-workers'' as a resource or as a demand).

Aligned with this relativistic perspective on the experience of work, Horan et al. (2020) and LePine (2022) explicitly articulate the need for future research to incorporate the \emph{appraisal process} into the challenge-hindrance stressor framework. In fact, Horan et al. (2020) state that ``\ldots stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees'' (p.~3). They go on to suggest future research continue to move away from \emph{a priori} classifications of demands, as doing so can be problematic for theoretical and empirical reasons.

Given the above, the first question we pose is whether workers exclusively experience job elements as resources, challenges, or hindrances, or whether a given job characteristic might be mutually considered as more than one of these (e.g., both a challenge and a resource). Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands (e.g., Bakker and Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011). For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance, and emotional demands as more of a challenge. Webster et al. (2011) approached this question with three commonly implicated workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as a challenge or hindrance, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees. We aim to both replicate the above findings and extend them to include resources.

@@

\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}

Both the job demands--resources model (Bakker and Demerouti, 2017) as well as the challenge--hindrance stressor framework (Cavanaugh et al., 2000) have been useful in the prediction of a wide variety of organizational outcomes including job satisfaction, motivation, commitment, and performance (e.g., LePine et al., 2005). Empirical work generally suggests that \emph{resources} are commonly associated with positive outcomes, including, most relevant for the current investigation, employee engagement. For example, Hakanen et al. (2008) found that job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, Bakker et al. (2007) found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource elements and engagement (e.g., Schaufeli, 2017).

@@

The findings regarding demands are more complex. When a demand is appraised as a hindrance, it is negatively associated with motivational resources (Kim and Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors, and job satisfaction (Cavanaugh et al., 2000). Chen et al. (2021) further found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Turnover intentions, actual turnover and withdrawal behaviors have also been associated with hindrance demands (Podsakoff et al., 2007). Appraising a demand as a \emph{challenge}, however, has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work, Chen et al. (2021), engagement, Crawford et al. (2010), and strain and turnover intentions, e.g., Abbas and Raja (2019)). Challenge appraisals have also been found to ehave negative associations with job search behaviors (e.g., Cavanaugh et al., 2000). Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas and Raja, 2019; LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between characteristic appraisals and important work outcomes. Given the differential relationships described above, and a focus on three outcomes (engagement, strain, and burnout) we make the following predictions (see Figure \ref{fig:ourmodel}):

@@

\section{Method}\label{method}

\subsection{Participants}\label{participants}

@@

\subsection{Materials}\label{materials}

\subsubsection{Characteristics, Challenge Demands, Hindrance Demands, and Resources}\label{characteristics-challenge-demands-hindrance-demands-and-resources}

@@

\subsubsection{Stress}\label{stress}

@@

\subsubsection{Burnout}\label{burnout}

@@

\subsubsection{Engagement}\label{engagement}

@@

\section{Results}\label{results}

Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes and Wilhelm, 2021). Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample.

@@

\subsubsection{Outcome Associations}\label{outcome-associations}

@@

\subsubsection{Challenges, Resources, and Job Outcomes}\label{challenges-resources-and-job-outcomes}

@@

\subsubsection{Hindrances, Resources, and Job Outcomes}\label{hindrances-resources-and-job-outcomes}

@@

Perceptions of resources and demands, broadly, are not universal -- there are individual differences in how employees experience job characteristics. This finding aligns quite well with the challenge-hindrance stressor framework, which posits that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus and Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000). Further, Cavanaugh et al. (2000) suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000), which we partially supported here.

Our results suggest that what is generally seen as a resource and challenge tends to be agreed upon more so that what is seen a hindrance. In fact, hindrance demands are rated more variably and thus, it may be important to have conversations about job characteristics and expectations at multiple time points after hire. For example, having open conversations with employees regarding their subjective perceptions of characteristics that may be unique in limiting their performance or comfort. Such conversations could happen during an annual performance review. In addition, LePine et al. (2005) and Podsakoff et al. (2007) encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands, which may be associated with increased performance in the short term, but strain when prolonged. The current results suggest that these activities and training sessions would ideally be personalized.

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{1}
\bibitem[\citeproctext]{ref-abbas2019challenge}
Abbas M and Raja U (2019) Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology} 34(2). Springer: 189--201.

\bibitem[\citeproctext]{ref-bakker2014job}
Bakker AB and Demerouti E (2014) Job demands--resources theory. \emph{Wellbeing: A complete reference guide}. John Wiley \& Sons, Ltd Chichester, UK: 1--28.

\bibitem[\citeproctext]{ref-bakker2017job}
Bakker AB and Demerouti E (2017) Job demands--resources theory: Taking stock and looking forward. \emph{Journal of occupational health psychology} 22(3). Educational Publishing Foundation: 273.

\bibitem[\citeproctext]{ref-bakker2013weekly}
Bakker AB and Sanz-Vergel AI (2013) Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior} 83(3). Elsevier: 397--409.

\bibitem[\citeproctext]{ref-bakker2005job}
Bakker AB, Demerouti E and Euwema MC (2005) Job resources buffer the impact of job demands on burnout. \emph{Journal of occupational health psychology} 10(2). Educational Publishing Foundation: 170.

\bibitem[\citeproctext]{ref-bakker2007job}
Bakker AB, Hakanen JJ, Demerouti E, et al. (2007) Job resources boost work engagement, particularly when job demands are high. \emph{Journal of educational psychology} 99(2). American Psychological Association: 274.

\bibitem[\citeproctext]{ref-burr2019third}
Burr H, Berthelsen H, Moncada S, et al. (2019) The third version of the copenhagen psychosocial questionnaire. \emph{Safety and health at work} 10(4). Elsevier: 482--503.

\bibitem[\citeproctext]{ref-campbell1959convergent}
Campbell DT and Fiske DW (1959) Convergent and discriminant validation by the multitrait-multimethod matrix. \emph{Psychological bulletin} 56(2). American Psychological Association: 81--105.

\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
Cavanaugh MA, Boswell WR, Roehling MV, et al. (2000) An empirical examination of self-reported work stress among US managers. \emph{Journal of applied psychology} 85(1). American Psychological Association: 65.

\bibitem[\citeproctext]{ref-chen2021daily}
Chen H, Wang H, Yuan M, et al. (2021) Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology} 12. Frontiers Media SA: 616002.

\bibitem[\citeproctext]{ref-crawford2010linking}
Crawford ER, LePine JA and Rich BL (2010) Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test. \emph{Journal of applied psychology} 95(5). American Psychological Association: 834.

\bibitem[\citeproctext]{ref-cronbach1951coefficient}
Cronbach LJ (1951) Coefficient alpha and the internal structure of tests. \emph{psychometrika} 16(3). Springer-Verlag: 297--334.

\bibitem[\citeproctext]{ref-demerouti2001job}
Demerouti E, Bakker AB, Nachreiner F, et al. (2001) The job demands-resources model of burnout. \emph{Journal of Applied psychology} 86(3). American Psychological Association: 499.

\bibitem[\citeproctext]{ref-gerich2017relevance}
Gerich J (2017) The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management} 24(3). Educational Publishing Foundation: 270.

\bibitem[\citeproctext]{ref-hakanen2008job}
Hakanen JJ, Schaufeli WB and Ahola K (2008) The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement. \emph{Work \& stress} 22(3). Taylor \& Francis: 224--241.

\bibitem[\citeproctext]{ref-horan2020review}
Horan KA, Nakahara WH, DiStaso MJ, et al. (2020) A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research. \emph{Frontiers in Psychology} 11. Frontiers Media SA: 560346.

\bibitem[\citeproctext]{ref-kim2020thriving}
Kim M and Beehr TA (2020) Thriving on demand: Challenging work results in employee flourishing through appraisals and resources. \emph{International Journal of Stress Management} 27(2). Educational Publishing Foundation: 111.

\bibitem[\citeproctext]{ref-kubicek2023all}
Kubicek B, Uhlig L, Hülsheger UR, et al. (2023) Are all challenge stressors beneficial for learning? A meta-analytical assessment of differential effects of workload and cognitive demands. \emph{Work \& Stress} 37(3). Taylor \& Francis: 269--298.

\bibitem[\citeproctext]{ref-lazarus1984stress}
Lazarus RS and Folkman S (1984) \emph{Stress, Appraisal, and Coping}. Springer publishing company.

\bibitem[\citeproctext]{ref-lepine2005meta}
LePine JA, Podsakoff NP and LePine MA (2005) A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance. \emph{Academy of management journal} 48(5). Academy of Management Briarcliff Manor, NY 10510: 764--775.

\bibitem[\citeproctext]{ref-lepine2022challenge}
LePine MA (2022) The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management} 47(2). SAGE Publications Sage CA: Los Angeles, CA: 223--254.

\bibitem[\citeproctext]{ref-peterson2001understanding}
Peterson NG, Mumford MD, Borman WC, et al. (2001) Understanding work using the occupational information network (o* NET): Implications for practice and research. \emph{Personnel psychology} 54(2). Wiley Online Library: 451--492.

\bibitem[\citeproctext]{ref-pindek2024dynamic}
Pindek S, Meyer K, Valvo A, et al. (2024) A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies. \emph{Journal of Business and Psychology}. Springer: 1--19.

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{O*NET, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications},
  pdfauthor={Alicia Stachowski2, John Kulas1, \& Renata García Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={O*NET, challenge-hindrance framework, job demands-resources, job characteristics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
\textbf{Purpose}: Discussions of job characteristics often include a tacit characterization that these job elements are either resources or demands. The purpose of this paper was to examine 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association with positive and negative outcomes, and 3) the potential buffering effect of resources on the relationships between demands and negative work outcomes. \textbf{Design/methodology/approach}: A sample of 568 respondents recruited from Prolific completed an online survey. They were asked to think only about their primary job, and each administered survey branched content dependent on whether this job could be described as consisting of the different O*NET job characteristics. They subsequently rated level of resource, challenge, or hindrance. \textbf{Findings}: Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, what is viewed as challenging is also commonly interpreted as resourceful. Furthermore, greater experienced resources moderate the challenge--engagement relationship as well as the hindrance-stress and hindrance--burnout relationships. \textbf{Originality/value}: We utilized a diverse sample of employees across industries who responded to items derived from O\emph{NET specifications. O}NET provides a rich and fairly exhaustive repository of job characteristics that also provides some consistency across investigations. We also explored characteristics at a higher level of aggregation (retaining O*NET category groupings), which again expands our collective knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work domains, as well as the relationships among them.
}

@@

\hypertarget{theoretical-foundations}{%
\subsection{Theoretical Foundations}\label{theoretical-foundations}}

Job demands-resources theory (e.g., Bakker \& Demerouti, 2014; 2017) highlights the importance of demands and resources on the employee experience of motivation and strain as well as other, less proximal outcomes. Resources include physical, psychological, social, or organizational aspects of jobs that help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001). The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).

Cavanaugh et al. (2000) extended this framework by proposing a distinction between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}. Challenge demands promote mastery, personal growth, and future gains. These demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility (M. A. LePine, 2022). Hindrance demands, in contrast, inhibit growth, learning, and the general achievement of goals. Example hindrance demands that have been previously noted include role conflict and role ambiguity (M. A. LePine, 2022).

M. A. LePine (2022) deconstructs the mechanisms by which demands are related to performance and wellbeing outcomes. First, demands appraised as \emph{challenges} typically result in a more positive appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Demands appraised as \emph{hindrances} elicit a different process. Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other negative affect--laden reactions (M. A. LePine, 2022).

Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, J. A. LePine et al. (2005) regarding performance and Crawford et al. (2010) regarding engagement). Pindek et al. (2024) meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by M. A. LePine (2022) above). As expected, hindrance demands had both direct and indirect (through strain) associations with performance (Pindek et al., 2024).

Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. Pindek et al. (2024) notes these \emph{a priori} classification of characteristics as demands, challenges, or hindrances as a methdological limitation, as do Horan et al. (2020). In fact, although much of our research on job demands is based on such exclusive classifications (Searle \& Auton, 2015), the most recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., two different employees could most certainly perceive ``daily interaction with co-workers'' as a resource or as a demand).

Aligned with this relativistic perspective on the experience of work, Horan et al. (2020) and M. A. LePine (2022) explicitly articulate the need for future research to incorporate the \emph{appraisal process} into the challenge-hindrance stressor framework. In fact, Horan et al. (2020) state that ``\ldots stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees'' (p.~3). They go on to suggest future research continue to move away from \emph{a priori} classifications of demands, as doing so can be problematic for theoretical and empirical reasons.

Given the above, the first question we pose is whether workers exclusively experience job elements as resources, challenges, or hindrances, or whether a given job characteristic might be mutually considered as more than one of these (e.g., both a challenge and a resource). Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011). For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance, and emotional demands as more of a challenge. Webster et al. (2011) approached this question with three commonly implicated workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as a challenge or hindrance, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees. We aim to both replicate the above findings and extend them to include resources.

@@

\hypertarget{connecting-appraisals-to-workplace-outcomes}{%
\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}}

Both the job demands--resources model (Bakker \& Demerouti, 2017) as well as the challenge--hindrance stressor framework (Cavanaugh et al., 2000) have been useful in the prediction of a wide variety of organizational outcomes including job satisfaction, motivation, commitment, and performance (e.g., J. A. LePine et al., 2005). Empirical work generally suggests that \emph{resources} are commonly associated with positive outcomes, including, most relevant for the current investigation, employee engagement. For example, Hakanen et al. (2008) found that job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, Bakker et al. (2007) found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource elements and engagement (e.g., Schaufeli, 2017).

@@

The findings regarding demands are more complex. When a demand is appraised as a hindrance, it is negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors, and job satisfaction (Cavanaugh et al., 2000). Chen et al. (2021) further found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Turnover intentions, actual turnover and withdrawal behaviors have also been associated with hindrance demands (Podsakoff et al., 2007). Appraising a demand as a \emph{challenge}, however, has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work, Chen et al. (2021), engagement, Crawford et al. (2010), and strain and turnover intentions, e.g., Abbas and Raja (2019)). Challenge appraisals have also been found to ehave negative associations with job search behaviors (e.g., Cavanaugh et al., 2000). Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas \& Raja, 2019; J. A. LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between characteristic appraisals and important work outcomes. Given the differential relationships described above, and a focus on three outcomes (engagement, strain, and burnout) we make the following predictions (see Figure \ref{fig:ourmodel}):

@@

\begin{verbatim}
##                _                                
## platform       x86_64-w64-mingw32               
## arch           x86_64                           
## os             mingw32                          
## crt            ucrt                             
## system         x86_64, mingw32                  
## status                                          
## major          4                                
## minor          3.1                              
## year           2023                             
## month          06                               
## day            16                               
## svn rev        84548                            
## language       R                                
## version.string R version 4.3.1 (2023-06-16 ucrt)
## nickname       Beagle Scouts
\end{verbatim}

\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

@@

\hypertarget{materials}{%
\subsection{Materials}\label{materials}}

\hypertarget{characteristics-challenge-demands-hindrance-demands-and-resources}{%
\subsubsection{Characteristics, Challenge Demands, Hindrance Demands, and Resources}\label{characteristics-challenge-demands-hindrance-demands-and-resources}}

@@

\hypertarget{stress}{%
\subsubsection{Stress}\label{stress}}

@@

\hypertarget{burnout}{%
\subsubsection{Burnout}\label{burnout}}

@@

\hypertarget{engagement}{%
\subsubsection{Engagement}\label{engagement}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021). Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample.

@@

\hypertarget{outcome-associations}{%
\subsubsection{Outcome Associations}\label{outcome-associations}}

@@

\hypertarget{challenges-resources-and-job-outcomes}{%
\subsubsection{Challenges, Resources, and Job Outcomes}\label{challenges-resources-and-job-outcomes}}

@@

\hypertarget{hindrances-resources-and-job-outcomes}{%
\subsubsection{Hindrances, Resources, and Job Outcomes}\label{hindrances-resources-and-job-outcomes}}

@@

Perceptions of resources and demands, broadly, are not universal -- there are individual differences in how employees experience job characteristics. This finding aligns quite well with the challenge-hindrance stressor framework, which posits that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus \& Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000). Further, Cavanaugh et al. (2000) suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000), which we partially supported here.

Our results suggest that what is generally seen as a resource and challenge tends to be agreed upon more so that what is seen a hindrance. In fact, hindrance demands are rated more variably and thus, it may be important to have conversations about job characteristics and expectations at multiple time points after hire. For example, having open conversations with employees regarding their subjective perceptions of characteristics that may be unique in limiting their performance or comfort. Such conversations could happen during an annual performance review. In addition, J. A. LePine et al. (2005) and Podsakoff et al. (2007) encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands, which may be associated with increased performance in the short term, but strain when prolonged. The current results suggest that these activities and training sessions would ideally be personalized.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
Bakker, A. B., Hakanen, J. J., Demerouti, E., \& Xanthopoulou, D. (2007). Job resources boost work engagement, particularly when job demands are high. \emph{Journal of Educational Psychology}, \emph{99}(2), 274.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.

\leavevmode\vadjust pre{\hypertarget{ref-burr2019third}{}}%
Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., Oudyk, J., Kristensen, T. S., Llorens, C., Navarro, A., et al. (2019). The third version of the copenhagen psychosocial questionnaire. \emph{Safety and Health at Work}, \emph{10}(4), 482--503.

\leavevmode\vadjust pre{\hypertarget{ref-campbell1959convergent}{}}%
Campbell, D. T., \& Fiske, D. W. (1959). Convergent and discriminant validation by the multitrait-multimethod matrix. \emph{Psychological Bulletin}, \emph{56}(2), 81--105.

\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
Cavanaugh, M. A., Boswell, W. R., Roehling, M. V., \& Boudreau, J. W. (2000). An empirical examination of self-reported work stress among US managers. \emph{Journal of Applied Psychology}, \emph{85}(1), 65.

\leavevmode\vadjust pre{\hypertarget{ref-chen2021daily}{}}%
Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.

\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
Crawford, E. R., LePine, J. A., \& Rich, B. L. (2010). Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test. \emph{Journal of Applied Psychology}, \emph{95}(5), 834.

\leavevmode\vadjust pre{\hypertarget{ref-cronbach1951coefficient}{}}%
Cronbach, L. J. (1951). Coefficient alpha and the internal structure of tests. \emph{Psychometrika}, \emph{16}(3), 297--334.

\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.

\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.

\leavevmode\vadjust pre{\hypertarget{ref-hakanen2008job}{}}%
Hakanen, J. J., Schaufeli, W. B., \& Ahola, K. (2008). The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement. \emph{Work \& Stress}, \emph{22}(3), 224--241.

\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
Horan, K. A., Nakahara, W. H., DiStaso, M. J., \& Jex, S. M. (2020). A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research. \emph{Frontiers in Psychology}, \emph{11}, 560346.

\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
Kim, M., \& Beehr, T. A. (2020). Thriving on demand: Challenging work results in employee flourishing through appraisals and resources. \emph{International Journal of Stress Management}, \emph{27}(2), 111.

\leavevmode\vadjust pre{\hypertarget{ref-kubicek2023all}{}}%
Kubicek, B., Uhlig, L., Hülsheger, U. R., Korunka, C., \& Prem, R. (2023). Are all challenge stressors beneficial for learning? A meta-analytical assessment of differential effects of workload and cognitive demands. \emph{Work \& Stress}, \emph{37}(3), 269--298.

\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.

\leavevmode\vadjust pre{\hypertarget{ref-lepine2005meta}{}}%
LePine, J. A., Podsakoff, N. P., \& LePine, M. A. (2005). A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance. \emph{Academy of Management Journal}, \emph{48}(5), 764--775.

\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
